Consistency scores in text data

### 2020-08-03 outputs/documents/paper.Rmd
notes on to-dos

However, n-gram models do not take the linguistic structure of language into account. For instance, @rosenfeld2000two [p. X]  **(Ke-Li add page please)** discusses language in this context, saying that '...it may as well be a sequence of arbitrary symbols, with no deep structure, intention or thought behind'. The prediction of the next word is based on only a few preceding words and broader context is not taken into account. Hence next-word prediction using n-gram based language models can be limited.

**(Ke-Li add brief write-up of implementation in R please. Probably quanteda unless there's a better option.)**

@@

**(Ke-Li add brief paragraph about negatives of this approach.)**

>>>>

However, n-gram models do not take the linguistic structure of language into account. For instance, @rosenfeld2000two [p. 1]  **(Ke-Li add page please)** discusses language in this context, saying that '...it may as well be a sequence of arbitrary symbols, with no deep structure, intention or thought behind'. The prediction of the next word is based on only a few preceding words and broader context is not taken into account. Hence next-word prediction using n-gram based language models can be limited.

**(Ke-Li add brief write-up of implementation in R please. Probably quanteda unless there's a better option.)**
The data set we used for training the n-gram model is [**(Ke-Li add a data set once settled the choice)**]. For generating n-grams, we used the Text Analysis Utilities (tau) R package to tokenize the training corpus into tri-grams.

@@

**(Ke-Li add brief paragraph about negatives of this approach.)**
#### Notes not content ####
- Inability to handle unknown or out-of-vocabulary (OOV) words.
- No shared representations at sub-word levels
- Word presentations are not contextual. Representation of apple is the same in context of fruit and tech company
- [Although these pre-trained embeddings can capture semantic meanings of words, they are context-free and fail to capture higher-level concepts in context, such as polysemous disambiguation, syntactic structures, semantic roles, anaphora.] (@hanretty2018comparing).

**(Ke-Li add brief write-up of implementation in R please.)** 
GloVe word embedding is available to operate in R with the text2vec package developed by Dmitriy Selivanov **(Ke-Li add package citation)**.
